Alex's Notes and Text Fragments for the JSS Manuscript

### 2023-08-11 paper/article.Rmd
cv -> repeated_cv

To define a resampling strategy, the `rsmp()` function is used to generate a resampling object using four folds and two repetitions following a random sampling logic ("cv").

>>>>

To define a resampling strategy, the `rsmp()` function is used to generate a resampling object using four folds and two repetitions following a random sampling logic ("repeated_cv").
